Extended Abstract

### 2021-05-24 paper/paper.tex
Add discussion section

% Typing rules
\usepackage{mathpartir}
\mprset {sep=0.5em} % Horizontal space between premises

@@

We start defining an untyped but well scoped \picalc{} using type-level de Bruijn indices \cite{deBruijn72} and embed a small expression language that handles composite sum and product types.
On top, we define a standard type system with linear and shared types using context-splits \autoref{type-system}.
We then provide an overview of how typing inference works, define constraint collection (\autoref{constraint-collection}) and constraint resolution (\autoref{constraint-resolution}), and state that both phases are sound and complete with regards to the type system defined in \autoref{type-system}.

We have proven that constraint collection is sound and (adapting McBride's work \cite{McBride03} to deal with intrinsically kinded terms) that the resolution of equality constraints is sound too.
The remaining proofs are still in progress.
(A note on notation: variables are black, \textcolor{blue}{types are blue}, \textcolor{olive}{constructors are green}, \textcolor{gray}{functions are gray}, and we are sorry this is not a poem.)

@@

\begin{mathpar}
%  \inferrule { \Gamma : \tCtx{n}{\gamma} \\ i : \Fin{n} \\ t : \ttype{\gamma} }
%             { \tVar{\Gamma}{i}{t} }

  \inferrule { \Gamma : \tCtx{n}{\gamma} \\ \tun{\Gamma} \\ t : \ttype{\gamma} }
             { \tVar{\Gamma,t}{\fzero}{t} }
             % \rulename{zero}

  \inferrule { \tVar{\Gamma}{i}{t} \\ s : \ttype{\gamma} \\ \tun{s} }
             { \tVar{\Gamma,s}{\fsuc~i}{t} }
             % \rulename{suc}

%  \inferrule { \Gamma : \tCtx{n}{\gamma} \\ e : \sExpr{n} \\ t : \ttype{\gamma}}
%             { \tExpr{\Gamma}{e}{t} }

  \inferrule { \tVar{\Gamma}{i}{t} } { \tExpr{\Gamma}{\svar~i}{t} }
             % \rulename{var}

  \inferrule { \tun{\Gamma} } { \tExpr{\Gamma}{\sunit}{\tunit} }
             % \rulename{unit}

@@

  \inferrule { \tExpr{\Gamma}{e}{t} } { \tExpr{\Gamma}{\sinl~e}{\tsum~t~s}}
             % \rulename{inl}

  \inferrule { \tSplit{\Gamma}{\Delta}{\Theta} \\ \tExpr{\Delta}{e}{s} \\ \tExpr{\Theta}{f}{t} }
             { \tExpr{\Gamma}{\spair~e~f}{\tprod~s~t}}
             %\rulename{pair}

%  \inferrule { \Gamma : \tCtx{n}{\gamma} \\ p : \sProc{n}}
%             { \tProc{\Gamma}{p} }

@@

  \inferrule { t : \ttype{\gamma} \\ \tProc{\Gamma , t}{p} } { \tProc{\Gamma}{\snew~p} }
             %\rulename{new}

  \inferrule { \tSplit{\Gamma}{\Delta}{\Theta} \\ \tExpr{\Delta}{e}{\tchan~\tone~\tzero~t} \\ \tProc{\Theta,t}{p} }
             { \tProc{\Gamma}{\srecv~e~p} }
             %\rulename{recv}

@@

>>>>

% Typing rules
\usepackage{mathpartir}
\mprset {sep=0.6em} % Horizontal space between premises

@@

We start defining an untyped but well scoped \picalc{} using type-level de Bruijn indices \cite{deBruijn72} and embed a small expression language that handles composite sum and product types.
On top, we define a standard type system with linear and shared types using context-splits \autoref{type-system}.
We then provide an overview of how typing inference works, define constraint collection (\autoref{constraint-collection}) and constraint resolution (\autoref{constraint-resolution}), and state that both phases are sound and complete with regards to the type system defined in \autoref{type-system}.
(A note on notation: variables are black, \textcolor{blue}{types are blue}, \textcolor{olive}{constructors are green}, \textcolor{gray}{functions are gray}, and we are sorry this is not a poem.)

@@

\begin{mathpar}
%  \inferrule { \Gamma : \tCtx{n}{\gamma} \\ i : \Fin{n} \\ t : \ttype{\gamma} }
%             { \tVar{\Gamma}{i}{t} }
  \inferrule { \Gamma : \tCtx{n}{\gamma} \\ \tun{\Gamma} \\ t : \ttype{\gamma} }
             { \tVar{\Gamma,t}{\fzero}{t} }
             % \rulename{zero}

  \inferrule { \tVar{\Gamma}{i}{t} \\ s : \ttype{\gamma} \\ \tun{s} }
             { \tVar{\Gamma,s}{\fsuc~i}{t} }
             % \rulename{suc}
%  \inferrule { \Gamma : \tCtx{n}{\gamma} \\ e : \sExpr{n} \\ t : \ttype{\gamma}}
%             { \tExpr{\Gamma}{e}{t} }

  \inferrule { \tVar{\Gamma}{i}{t} } { \tExpr{\Gamma}{\svar~i}{t} }
             % \rulename{var}
  %\inferrule { \tun{\Gamma} } { \tExpr{\Gamma}{\sunit}{\tunit} }
             % \rulename{unit}

@@

  \inferrule { \tExpr{\Gamma}{e}{t} } { \tExpr{\Gamma}{\sinl~e}{\tsum~t~s}}
             % \rulename{inl}
  %\inferrule { \tSplit{\Gamma}{\Delta}{\Theta} \\ \tExpr{\Delta}{e}{s} \\ \tExpr{\Theta}{f}{t} }
  %           { \tExpr{\Gamma}{\spair~e~f}{\tprod~s~t}}
             %\rulename{pair}
%  \inferrule { \Gamma : \tCtx{n}{\gamma} \\ p : \sProc{n}}
%             { \tProc{\Gamma}{p} }

@@

  \inferrule { t : \ttype{\gamma} \\ \tProc{\Gamma , t}{p} } { \tProc{\Gamma}{\snew~p} }
             %\rulename{new}
  %\inferrule { \tSplit{\Gamma}{\Delta}{\Theta} \\ \tExpr{\Delta}{e}{\tchan~\tone~\tzero~t} \\ \tProc{\Theta,t}{p} }
  %           { \tProc{\Gamma}{\srecv~e~p} }
  %           %\rulename{recv}

@@

\section{Discussion}

We have outlined a procedure for decidable type checking and inference of a \picalc{} with linear and shared types.
Constraint collection and constraint resolution are kept separate, and their metatheory allows for deferred constraints.
We have proven in Agda that constraint collection and the resolution of equality constraints is sound, the remaining proofs are still in progress.
